---
title: "class4"
author: "NanJia"
date: "2/3/2022"
output:
  html_document: default
  word_document: default
  pdf_document: default
urlcolor: blue  
---
<!-- This is a comment in HTML/RMarkdown -->

<!-- You need to install MikTex on a PC or MacTex on a Mac to create PDF files.
     - In the MikTex installation: 
       - set paper to "Letter" (not A4)
       - set Install Missing Packages on the Fly to "Yes" (not Ask Me First)
       - keep automatic updates checkbox checked
     
     The first time you create a PDF file using KnitR will be VERY slow
       because MikTex is updating -- it will be much faster the second time
--> 


<!-- Sets the Working directory to be RStudio Project folder 
     (this is not the default in KnitR) -->
```{r setup, include=FALSE, cache = FALSE}
require("knitr") 
## setting working directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

<!-- Runs the code but does not output to the document (include=FALSE) -->
```{r include=FALSE}
source(file="scripts/ggp-app04.R");
```

Things you can do in RMD:  
**Bold**  
*Italics*  
***Bold/Italics***  

Headers must have a **blank line** before in order to work.  

# R markdown for Class 4

## It is a test

### Note:
You can go up to Header 6... I think you see the pattern!

## Embedded R code
You can embed R code and output in this document using 
`r weatherData$avgTemp[1:10]`  everything between the apostrophes is treated as script.  So, you can also output the average temp `r sum(weatherData$avgTemp)`.  You can use anything from your script!

***

## Including Plots

You can also embed plots, for example:

```{r echo=FALSE}
plot(plot1)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot. 
